Alzheimer_PUDN

### 2024-02-12 ArticleMethodo.Rmd
Mis à jour du nuage de mots
Sans "alzheimer", "maladie", "disease".
Palette : colors = viridis_pal()(6)

nuage_corpus_clean<-tm_map(nuage_corpus,tolower)
nuage_corpus_clean<-tm_map(nuage_corpus_clean,removeNumbers)
nuage_corpus_clean<-tm_map(nuage_corpus_clean,removeWords,stopwords("english")) nuage_corpus_clean<-tm_map(nuage_corpus_clean,removeWords,stopwords("fr")) nuage_corpus_clean<-tm_map(nuage_corpus_clean,removeWords,"alzheimer") 
nuage_corpus_clean<-tm_map(nuage_corpus_clean,removePunctuation)
nuage_corpus_clean<-tm_map(nuage_corpus_clean,stripWhitespace)

wordcloud(nuage_corpus_clean,max.words = 100, min.freq =1, colors = brewer.pal(8, "Dark2"), rot.per=0.35)
```

>>>>

nuage_corpus_clean<-tm_map(nuage_corpus,tolower)
nuage_corpus_clean<-tm_map(nuage_corpus_clean,removeNumbers)
nuage_corpus_clean<-tm_map(nuage_corpus_clean,removeWords,stopwords("english"))
nuage_corpus_clean<-tm_map(nuage_corpus_clean,removeWords,stopwords("fr"))
nuage_corpus_clean<-tm_map(nuage_corpus_clean,removeWords, c("alzheimer", "maladie", "disease"))
nuage_corpus_clean <- tm_map(nuage_corpus_clean, content_transformer(function(x) gsub("[[:punct:]]", "", x)))
nuage_corpus_clean<-tm_map(nuage_corpus_clean,removePunctuation)
nuage_corpus_clean<-tm_map(nuage_corpus_clean,stripWhitespace)

wordcloud(nuage_corpus_clean,max.words = 100, min.freq =1, colors = viridis_pal()(6), rot.per=0.35)
